QPLIB: A Library of Quadratic Programming Instances

### 2018-02-02 AnswerToTheReferees.tex

\item The taxonomy in Section 2.2.1 seems to be unaware of the fact that an indefinite Hessian does not mean that a problem is difficult. For example, saddle-point problems such as

$$ \begin{bmatrix}
G & A^T\\
A & 0
\end{bmatrix}
\begin{pmatrix}
x \\
z 
\end{pmatrix}
=
\begin{pmatrix}
-g \\
b 
\end{pmatrix}
$$

can be solved to global optimality as long as the matrix is second-order sufficient. This means
that even some QPs with indefinite Hessians can easily be solved to global optimality.

\rep{Thank you for having raised this point. We addressed in Sections 2.2.1 and 2.2.2.
%TODO:Antonio. 
%lo dicevamo già a p. 10, ma grazie per avercelo ricordato: adesso lo richiamiamo brevemente in §2.2.1 e lo discutiamo in §2.2.2
%
%\leo{cosa vuol dire? Questa condizione si puo` testare in polytime? Sicuramente puo` entrare nel discorso a risposta dei punti 2-4 del referee \#1.} 
}

@@

\item The discussion on p.9 recounts some textbook facts, and is largely superfluous. Delete it.

\rep{
Although all the facts recalled in §2.2.2 are in fact well known, we still feel they need be discussed in this context because they illustrate how the taxonomy (as almost all of them) has some grey areas whereby the same underlying problem can be described by instances that would be classified differently. This is, as the header of the section recalls, strongly tied to the concept of reformulation. One relevant example is the relationship between definiteness of the Hessians and convexity, correctly pointed out by the referee, which is naturally discussed in §2.2.2. One of the nontrivial choices in our library is that we made no effort to reformulate the instances (although of course we could have), and inserted them in the library in the very same format they have been provided to us by the original contributors. Section 2.2.2 is crucial in justifying this choice, as it shows that there are several degrees of freedom to move the instances from one class to another. Doing so, however, is typically justified by the fact that this makes one specific solver more efficient in solving them, a bias that we don't want to add. Hence, we have chosen to keep the instances in their ``natural'' format, this being the one in which the original contributor initially wrote them.
%TODO: Antonio.
%\leo{cancelliamo tutto!} 
%As requested, aliminated the discussion from the manuscript
}

@@

\item The description of NLP solvers in Section 2.3.2 is at somewhat misleading. For example, KNI-
TRO is also a primal-dual interior-point method, not just a barrier code (in fact primal-dual
methods are preferred). The description of the “active-set” methods is wrong, unless you refer
to the inner method, namely the active-set QP solves. Otherwise, SNOPT and KNITRO are
SQP methods, while CONOPT is a gradient-projection method, and MINOS is an augmented
Lagrangian method. You must correct this section

\rep{TODO: Stefan and Ambros
%\leo{correggiamo gli errori e ringraziamo il referee} 
}

\item Some classes of problems in Table 4 do not seem to have many instances. Please create more.

\rep{We followed your suggestion and we gathered several additional instances and we included to the final version of the library (see the reply to the AE for further details).}

### 2018-02-02 QPLIB-3.tex
Update QPLIB-3.tex

>>>>

\textcolor{red}{
One of the nontrivial choices in our library is that we made no effort to reformulate the instances, and inserted them in the library in the very same format they have been provided to us by the original contributors. Section \ref{ssec:reform} is crucial in justifying this choice, as it shows that there are several degrees of freedom to move the instances from one class to another. Tailoring the structure of a problem to the solver is, however, a bias we do not want to add.
}
